Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-11-25 Scripts/Initial_Analysis.Rmd
Final edits before sending  to comm.

```{r Time_lapse_plot}

#### Both plots for tresh one
#  Embarrasing coding Juliano!

ggplot() +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            # alpha= 1,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            # alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  # Shameslly plot it again to fix colors
  geom_area(data = subset(plot_data, level == "stock" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              # x = reorder(as.numeric(taxon_emer),level),
              y = value,
              fill = level
            ),
            # alpha= 1,
            size=0.5,
            colour="black"
  )  +
  # geom_line(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = as.numeric(taxon_emer),
  #             y = total,
  #             fill = level
  #           ),
  #           colour="grey30",
  # )  +
  # geom_text(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = 2037,
  #             y = total+5,
  #             label = label
  #           ),
  #           size = 3,
  #           colour="grey30",
  #           hjust=0.6,
  # )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  scale_y_continuous("",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right",
    strip.text.x = element_blank(),
    panel.spacing = unit(3, "lines") # space between plots
  ) +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
  width = 10,
  height = 5,
  units = "in"
  )

@@

# Plot the bubbles!
ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = log_value,
      size = n_taxa,
      colour = un_geo_region,
      shape = un_geo_region
    ),
    alpha = 0.7
  ) +
  # Divisory lines
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(data = Percentile_value,
             aes(yintercept = x),
             color = "grey90"
  )  +
  # right side labels
  geom_label_repel(data = subset(Buble_data, mean_yr > 2035 & sum_value_bi >= 1),
                  aes(
                    x = mean_yr,
                    y = log_value,
                    label = sau_fishing_entity
                  ),
                  arrow = arrow(length = unit(0.009, "npc"),
                                type = "closed",
                                ends = "first"),
                  force = 2,
                  box.padding = 0.2,
                  fill = "NA",
                  nudge_x = 2050 + subset(Buble_data, mean_yr > 2035 & sum_value_bi >= 1)$mean_yr,
                  segment.size  = 0.2,
                  segment.color = "grey50",
                  direction     = "y",
                  hjust         = 1
  ) +
  # right side labels
  geom_label_repel(data = subset(Buble_data, mean_yr < 2035 & sum_value_bi >= 1),
                  aes(
                    x = mean_yr,
                    y = log_value,
                    label = sau_fishing_entity
                  ),
                  arrow = arrow(length = unit(0.009, "npc"),
                                type = "closed",
                                ends = "first"),
                  force = 1,
                  box.padding = 0.2,
                  fill = "NA",
                  nudge_x = 2010 - subset(Buble_data, mean_yr < 2035 & sum_value_bi >= 1)$mean_yr,
                  segment.size  = 0.2,
                  segment.color = "grey50",
                  direction     = "y",
                  hjust         = 1
  ) +
  geom_text(data = Labels_data,
            aes(
              x = x,
              y = y,
              label = label
            ),
            size = 3,
            color = "grey30"
  ) +
  scale_shape("Region") +
  scale_color_viridis(name="Region",
                      discrete = T) +
  scale_x_continuous("Average time of emergence",
                     limits = c(2000,2080),
                     breaks = seq(2000,2080,10)
  ) +
  scale_y_continuous("Fishing revenue (log10)",
                     limits = c(-6,2),
                     breaks = seq(-6,2,2),
                     expand = c(0,0)
  ) +
  scale_size("Number of\nemerging stock") +
  ggsave("./Figures/bubble_plot.png",
         width = 8,
         height = 8,
         units = "in"
  )

>>>>

```{r Time_lapse_plot, eval = T, echo = F}

### Three plots

count_eez_plot <- ggplot() +
  geom_area(data = subset(plot_data, metric == "com_sum" & level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  )  +
  scale_y_continuous("Cumulative number of EEZs (n)",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     # label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(legend.position = "") +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.1
  )

#### Count stock plot 
count_stock_plot <- ggplot() +
  geom_area(data = subset(plot_data, metric == "com_sum" & level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  )  +
  scale_y_continuous("Cumulative number of stocks (n)",
                     expand = c(0,0)
                     ) +
  scale_x_continuous("Time of emergence of transboundary index",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     # label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(legend.position = "") +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.7, 
                     end = 0.7
  )

# Percentage plot
percentage_plot <- ggplot() +
  geom_area(data = subset(plot_data, level == "eez" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  ) + 
  geom_area(data = subset(plot_data, level == "stock" & my_facet == "Percentage (%)"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            size=0.5,
            colour="black"
  ) + 
  scale_y_continuous("Cumulative proportion of the total (%)",
                     expand = c(0,0)
  ) +
  scale_x_continuous("",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     # label = c(seq(2000,2075,25),">2100"),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right",
    strip.text.x = element_blank()
  ) +
  guides(fill=guide_legend(title= "Level", reverse=FALSE)) +
  scale_fill_viridis(discrete = T,
                     begin = 0.1, 
                     end = 0.7,
                     labels = c("EEZs","Stocks")
  )

# Legend
  legend <- get_legend(percentage_plot)

  percentage_plot <- percentage_plot + 
    theme(legend.position = "")

# Draw figure
  plot_all <- ggdraw() +
    # Latin America and the Car.
    draw_plot(count_eez_plot, x = 0.01, y = 0, width = 0.28, height = 1) +
    # Europe
    draw_plot(count_stock_plot, x = 0.28, y = 0, width = 0.28, height = 1) +
    # Percentage plot
    draw_plot(percentage_plot, x = 0.56, y = 0 , width = 0.28, height = 1) +
    # legend
    draw_plot(legend, x = 0.84, y = 0 , width = 0.28, height = 1)

  # Save plot
  save_plot(
    "./Figures/cumu_per_freq.png",
    plot_all,
    base_height = 5,
    base_width = 12
  )

@@

# Plot the bubbles!
ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = log_value,
      size = n_taxa,
      colour = un_geo_region,
      shape = un_geo_region
    ),
    alpha = 0.7
  ) +
  # Divisory lines
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(data = Percentile_value,
             aes(yintercept = x),
             color = "grey90"
  )  +
  # right side labels
  geom_label_repel(data = subset(Buble_data, mean_yr > 2035 & sum_value_bi >= 1),
                  aes(
                    x = mean_yr,
                    y = log_value,
                    label = sau_fishing_entity
                  ),
                  arrow = arrow(length = unit(0.009, "npc"),
                                type = "closed",
                                ends = "first"),
                  force = 2,
                  box.padding = 0.2,
                  fill = "NA",
                  nudge_x = 2050 + subset(Buble_data, mean_yr > 2035 & sum_value_bi >= 1)$mean_yr,
                  segment.size  = 0.2,
                  segment.color = "grey50",
                  direction     = "y",
                  hjust         = 1
  ) +
  # right side labels
  geom_label_repel(data = subset(Buble_data, mean_yr < 2035 & sum_value_bi >= 1),
                  aes(
                    x = mean_yr,
                    y = log_value,
                    label = sau_fishing_entity
                  ),
                  arrow = arrow(length = unit(0.009, "npc"),
                                type = "closed",
                                ends = "first"),
                  force = 1,
                  box.padding = 0.2,
                  fill = "NA",
                  nudge_x = 2010 - subset(Buble_data, mean_yr < 2035 & sum_value_bi >= 1)$mean_yr,
                  segment.size  = 0.2,
                  segment.color = "grey50",
                  direction     = "y",
                  hjust         = 1
  ) +
  geom_text(data = Labels_data,
            aes(
              x = x,
              y = y,
              label = label
            ),
            size = 3,
            color = "grey30"
  ) +
  scale_shape("Region") +
  scale_color_viridis(name="Region",
                      discrete = T) +
  scale_x_continuous("Average time of emergence",
                     limits = c(2000,2080),
                     breaks = seq(2000,2080,10)
  ) +
  scale_y_continuous("Fishing revenue (log10)",
                     limits = c(-6,2),
                     breaks = seq(-6,2,2),
                     expand = c(0,0)
  ) +
  scale_size("Number of\nemerging stock") +
  ggsave("./Figures/bubble_plot.png",
         width = 12,
         height = 8,
         units = "in"
  )
